The KMOS Deep Survey (KDS): dynamical measurements of $z\sim3.5$ main sequence galaxies\thanks{Based on observations obtained at the Very Large Telescope of the European Southern Observatory. Programme IDs: }

### 2017-03-21 paper.tex
March 21

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
%\author[O.J. Turner et al.]{
%O. J. Turner,$^{1,2,\thanks{E-mail: turner@roe.ac.uk (OJT)}}$
%R. K. Cochrane,$^{1}$
%M. Cirasuolo,$^{1,2}$
%C. M. Harrison,$^{2,3}$
%J. Dunlop,$^{1}$\newauthor
%R. J. McLure,$^{1}$
%A. M. Swinbank$^{4,3}$
%H. L. Johnson$^{3,4}$
%\\
%$^{1}$SUPA\thanks{Scottish Universities Physics Alliance}, Institute for Astronomy, University of Edinburgh, Royal Obervatory, Edinburgh EH9 3HJ\\
%$^{2}$European Southern Observatory, Karl-Schwarzschild-Str. 2, 85748 Garching b. M{\"u}nchen, Germany\\
%$^{3}$Centre for Extragalactic Astronomy, Durham University, South Road, Durham, DH1 3LE, U.K.\\
%$^{4}$Institute for Computational Cosmology, Durham University, South Road, Durham, DH1 3LE, U.K.
%}

@@

The picture is complicated by the addition of major and minor galaxy mergers which can rapidly change the physical properties of galaxies \citep[e.g.][]{Toomre1977,Lotz2008,Conselice2011,Conselice2014} and the relative importance of in-situ, secular stellar mass growth vs. stellar mass aggregation via mergers is the subject of much work involving both observations and simulations \citep[e.g.][]{Robaina2009,Kaviraj2012,Stott2013,Lofthouse2016,Qu2016}. 
To account for the growing number density of quiescent galaxies from z$\sim 2.5$ to the present day \citep[e.g.][]{Bell2004,Faber2007,Brown2007,Ilbert2010,Brammer2011,Muzzin2013,Buitrago2013} there must also be some process which shuts off star-formation within main sequence galaxies (i.e. quenching) which, to explain observations, is a function of both mass and environment \citep{Peng2010,Darvish2016}.

Recent cosmological volume simulations are able to resolve the complex interplay of baryonic processes which are at work as galaxies evolve, and can track the development of individual galaxies from early stages, to maturity and through quenching \citep{Dubois2014a,Vogelsberger2014b,Schaye2015}.
Observations can aid the predictive power of such simulations by providing constraints on the evolving physical properties of galaxy populations.
The observed dynamical properties of galaxies contain information about the transfer of angular momentum between dark matter halos and the baryons and the dissipation of this angular momentum thereafter (through gravitational collpase, mergers and outflows \citealt{Fall1983,Romanowsky2012,Fall2013}), constituting an important set of quantities for simulators to attempt to match.
Developments in both Integral-Field Spectroscopy (IFS) instrumentation and data analysis tools over the last decade have led to the observation of two-dimensional velocity and velocity dispersion fields for large samples of galaxies of different morphological types, spanning a wide redshift range \citep[e.g.][]{Sarzi2005,Flores2006,Epinat2008,ForsterSchreiber2009,Cappellari2011,Gnerucci2011,Epinat2012,Croom2012,Swinbank2012,Swinbank2012a,Bundy2015,Wisnioski2015,Stott2016,Harrison2017,Swinbank2017} and when interpreted in tandem with high-resolution imaging data from the Hubble Space Telescope ({\em {\em HST}}) these data provide exquisite information about the range of physical processes which are driving galaxy evolution.
In particular, in recent years the multiplexing capabilities of KMOS \citep{Sharples2013} have allowed for IFS kinematic observations for large galaxy samples to build up over much shorter timescales \citep{Sobral2013,Wisnioski2015,Stott2016,Mason2016,Harrison2017} providing an order of magnitude boost in statistical power over previous high-redshift campaigns.

SFGs generally appear to be increasing in random motions with increasing redshift between $0 < z < 3$, as traced by their observed velocity dispersions, $\sigma_{obs}$ \citep{Genzel2008,ForsterSchreiber2009,Law2009,Cresci2009,Gnerucci2011,Epinat2012,Kassin2012,Green2014,Wisnioski2015,Stott2016}.
This has been explained in terms of increased `activity' in galaxies during and before the global peak in cosmic SFRD \citep{Madau_2014}, in the form of higher specific star formation rates (sSFR) \citep{Wisnioski2015}, larger gas reservoirs \citep{Law2009,ForsterSchreiber2009,Wisnioski2015,Stott2016}, more efficient accretion \citep{Law2009}, increased stellar feedback from supernovae \citep{Kassin2012} and turbulent disk instabilities \citep{Law2009,Bournaud2007,Bournaud2016}, all of which combine to increase $\sigma_{obs}$ and complicate its interpretation.

@@

This paper focusses on the third question by deriving and interpreting the spatially resolved kinematics of the KDS galaxies, particularly the rotation velocities and velocity dispersions, using the [O~{\sc III}]$\lambda$5007 emission line, discussing what we can learn about the nature of galaxy formation at $z \sim 3.5$ and forming evolutionary links with lower redshift work.
We seek also to minimise the impact of systematic differences introduced by the differing approaches in defining and extracting kinematic parameters when interpreting these trends.  
By making use of KMOS we have been able to study [O~{\sc III}]$\lambda$5007 emission in 77 galaxies with integration times ranging between 7.5-9 hours on source, with these galaxies, which span the mass range $9.5 < log(M_{\star}[M_{\odot}]) < 10.5$, marking a leap in the statistics of galaxies observed in IFS at $z > 3$. \\

@@

\subsubsection{GOODS-S}\label{subsubsec:sample_selection_goods}
Two of the FIELD environment pointings (GOODS-S-P1;GOODS-S-P2; see Table \ref{tab:pointings}) are selected within GOODS-S region \citep{Guo2013}; accessible from the VLT and with excellent multi-wavelength coverage, including deep {\em HST WFC3 F160W} imaging with $ 0.06^{\prime\prime}$ pixel scale and $ \sim 0.2^{\prime\prime}$ PSF, which is well suited for constraining galaxy morphology \citep{Grogin2011,Koekemoer2011}.
We select targets from the various spectroscopic campaigns which have targetted GOODS-S, including measurements from VIMOS \citep{Balestra2010,Cassata2014}, FORS2 \citep{Vanzella2005,Vanzella2006,Vanzella2008} and both LRIS and FORS2 as outlined in \cite{Wuyts2009}.
These targets must be within the redshift range $3 < z < 3.8$, have high spectral quality (as quantified by the VIMOS redshift flag equal `3' or `4', and the FORS2 quality flag equal `A') and we carefully exclude those targets for which the [O~{\sc III}]$\lambda$5007 or H$\beta$ emission lines, observable in the K-band at these redshifts, would be shifted into a spectral region plagued by strong OH emission.
The galaxies which remain after imposing these criteria are distributed across the GOODS-S field, and we select two regions where $\sim 20$ targets can be allocated to the KMOS IFUs (noting that the IFUs can patrol a $7.2^{\prime}$ diameter patch of sky during a single pointing).
In GOODS-S-P1 and GOODS-S-P2 we observe 20 and 17 galaxies respectively.\footnote{We note that the number of observed galaxies in GOODS-S-P2 does not include two targets which were later found to have $z < 0.5$.}

\subsubsection{SSA22}\label{subsubsec:sample_selection_ssa}
A single CLUSTER environment pointing (SSA22-P1; see Table \ref{tab:pointings}) is selected from the SSA22 field, \citep{Steidel1998,Steidel2000,Steidel2003,Shapley2003}, which, as mentioned above, is an overdensity of LBG candidates at $z \sim 3.09$.
Thousands of spectroscopic redshifts have been confirmed for these LBGs with follow up observations using LRIS \citep{Shapley2003,Nestor2013}.
A combination of deep {\em B,V,R} band imaging with the Subaru Suprime-Cam \citep{Matsuda2004}, deep narrow band imaging at 3640$\AA$ \citep{Matsuda2004} and at 4977$\AA$ \citep{Nestor2011} and archival {\em HST ACS} and {\it WFC3} provides ancillary data in excellent support of integral field spectroscopy, albeit over a shorter wavelength baseline and with shallower exposures than in the GOODS-S field.
Fortunately at $z \sim 3.09$ the [O~{\sc III}]$\lambda$5007 line is shifted into a region of the K-band which is free from OH features and so for the CLUSTER environment pointing we fill the KMOS IFUs with galaxies located towards the centre of the SSA22 protocluster (SSA22-P1).

@@

We plot the relationship between $V_{C}$ and $M_{\star}$ for the isolated field sample in the left panel of Figure \ref{fig:tf_relation}.
In \cite{Harrison2017}, the inverse stellar mass Tully-Fisher relation relation is fit to $\sim400$ $9.5 < log(M_{\star}[M_{\odot}]) < 10.5$ star-forming galaxies at $z\sim0.9$, measured to be rotationally dominated with $V_{C}/\sigma_{int} > 1$.
The data are used to constrain parameters `a' and `b' in the equation $logV_{C}=b+a[logM_{\star} - 10.0]$ (see their section 4.2) finding $a = 0.33 \pm 0.11$ and $b = 2.12 \pm 0.04$.
We plot this best fit relation with the solid green line, with the green shaded region giving the typical scatter of 0.2 dex along the velocity axis.
These $z\sim0.9$ parameters are consistent with the coefficients measured in the local universe, $a_{z=0} = 0.278 \pm 0.010$ and $b_{z=0} = 2.142 \pm 0.004$ \citep{Reyes2011}, for a sample of $z<0.1$ disks in a similar mass range to KROSS and traced with H$\alpha$ emission.
In \citep{Reyes2011} $V_{C}$ has been extracted at the same radius and we plot this $z\sim 0.1$ local relation as the dashed black line in the left panel of Figure \ref{fig:tf_relation}.
The agreement between these parameters derived at $z\sim0$ and $z\sim0.9$ suggests that there is no evolution of the slope/normalisation of the stellar mass Tully-Fisher relation for rotationally dominated star-forming galaxies between these limits. \\

@@

Throughout \cref{sec:results} we have investigated the derived kinematic parameters of the isolated field sample, showing first that within the scatter the rotation dominated galaxies sit on a rotation velocity - stellar mass relationship consistent with what is observed in the local universe.
The mean rotation velocity of the isolated field sample is low as a result of averaging over a sample containing a large number of dispersion dominated galaxies ($66\%$ of the sample).
This increased number of dispersion dominated galaxies in comparison to at low and intermediate redshifts appears to be driven by high velocity dispersions at $z\sim3.5$.
In this section we discuss possible physical origins for the elevated random motions traced by $\sigma_{int}$ and their impact on the galactic dynamics.

@@

The $\sigma_{int}$ shifted galaxies in Figure \ref{fig:sigma_shifted} are consistent with a single relation for the increase in velocity dispersion with redshift as a result of increasing gas fractions, with the difference between the slopes in the left and right panels highlighting the role of stellar mass in the kinematic settling of galaxies between $z\sim2$ and the local universe. 
The isolated field sample data, in combination with comparison sample results spanning $z=0-3$, thus suggest that the time evolution of the velocity dispersion measured from ionised gas emission lines is intimately linked to the consumption of gas and the accumulation of stars in a stable disk \citep[e.g.][]{Law2009,Law2012b,Law2012c,Wisnioski2015}.
Rotation dominated galaxies become less representative of the typical star-forming population at these redshifts as a result of the increased velocity dispersions as shown in Figure \ref{fig:rdf_and_v_sigma_w_redshift}, constituting only $\sim1/3$ of the isolated field sample at $z\sim3.5$.
This suggests we are probing more chaotic and unstable systems subject to gravitational instabilities and collapse on the disk scale \citep{Burkert2010,Genzel2011}, residing in a much more active period of the universe in terms of both accretion and star-formation.
Recent results indicate that these systems become strongly baryon-dominated on the galaxy disk scale at high redshift, which may imply that the increasing contribution of dark matter to galaxy disks with decreasing redshift plays a role in the evolution of velocity dispersions.

The precise interpretation of the velocity dispersion remains unclear, although there is mounting evidence that random motions have an increasingly significant contribution to the mass budget of high-redshift galaxies \citep[e.g.][]{Kassin2007,Law2009,Burkert2010,Kassin2012,Wuyts2016b,Lang2017,Ubler2017,Genzel2017}.
The nature of dispersion dominated galaxies at high-redshift has been discussed in \cite{Newman2013} using Adaptive-Optics (AO) and seeing limited observations of the same galaxies.
The AO observations shows that in some cases galaxies which are clasified as dispersion dominated with seeing limited observations reveal much larger velocity gradients at higher spatial resolution.
This highlights that beam-smearing effects can wash-out observed rotational motions, particularly for small galaxies.
We have attempted to account for beam smearing using half-light radius and velocity gradient dependent dynamical modelling, but we acknowledge that these observations are challenging and cannot rule out the presence of unresolved velocity gradients in our seeing-limited dataset.
Smaller galaxies do have intrinsically smaller rotation velocities, whilst there is no observed dependence of velocity disperion on galaxy size \citep[e.g.][]{Newman2013}.
Dispersion dominated galaxies are therefore likely to be at an earlier evolutionary stage and unstable to gravitational instabilities which generate turbulence which is then maintained by the potential energy of the gas in the disk \citep{Burkert2010,Newman2013}.

@@

In sum, the isolated field sample galaxies are diverse and kinematically premature, with $\sim2/3$ of the sample being dominated by random motions which may contribute to supporting a portion of the dynamical mass \citep[e.g.][]{Kassin2007,Cresci2009,Burkert2010,Gnerucci2011,Kassin2012,Newman2013,Straatman2017,Ubler2017,Lang2017}.
In the context of the equilibrium model explored here, these galaxies will evolve gradually with redshift along the velocity-mass relationship into stable disk galaxies which have converted their gas reservoirs into stellar mass \citep[e.g.][]{Lilly2013,Tacconi2013,Wisnioski2015,Tacconi2017}. 
Future work at higher resolution and redshift will trace the extent to which gas-derived velocity dispersions trace the stellar dispersions and will investigate even earlier and more chaotic stages in the lifetimes of late-type galaxies.

@@

\begin{table*}
\centering
\begin{threeparttable}
\caption{We present here a reference of the mean and median kinematic properties used throughout figures \protect\ref{fig:rdf_and_v_sigma_w_redshift} and \protect\ref{fig:sigma_and_v_sigma_w_redshift} for the different surveys.
The errors on the mean represent the statistical errors from bootstrap resampling and the lower and upper errors on the medians are the 16th and 84th percentiles of the distribution respectively.}
\label{tab:evolution_numbers}
\begin{tabular}{c c c c c c c c c c }

@@

We make use of tabulated data from the surveys deemed directly comparable, where available, to compute sample averages using the following method. 
Throughout \cref{sec:results} we highlight in the figures which values can be directly compared using filled and hollow symbols.
The fractional error weighted mean of $V_{C}/\sigma_{int}$, $\sigma_{int}$ and $V_{C}$ in each of the samples is computed (i.e. we do not want the derived values with extremely large errors to dominate the averages).
The errors on these mean values are computed in a statistical sense, by generating bootstrapped samples, with replacement, with size equivalent to the original survey sample size and with values perturbed by a random number drawn from a gaussian distribution with width given by the error on the original point.
The same process is applied to compute the errors on the sample medians and we report the 16th and 84th percentiles of the distributions of each of the above quantities as an indicator of the distribution width, and hence galaxy diversity, at each redshift slice.
These results are listed in Table \ref{tab:evolution_numbers} and discussed in detail throughout \cref{subsec:redshift_evolution}, where we will make statements about dynamical evolution by connecting the dots of these different surveys, assuming that on average they are tracing a population of SFGs which evolve across cosmic time.

@@

\subsection{DYNAMO ($z\sim0.1$, but selected with physical properties resembling $z\sim2$)}\label{subsec:DYNAMO}
In the DYNAMO survey \citep[G14]{Green2014}, H$\alpha$ IFU data of 67 galaxies with median $log(M_{\star}[M_{\odot}])=10.3$ at $z\sim0.1$ is presented.
The selection criteria is such that half of the sample have high sSFR representative of SFGs at $z\sim 2$, and are also found to have higher $f_{gas}$ values than locally, mimicking the physical conditions of $z\sim 2$ SFGs.
$V_{C}$ values are extracted at a fixed radius from an arctangent model fit to the velocity fields ($1.6R_{1/2}$ as measured in the r-band) and $\sigma_{int}$ is taken as the luminosity weighted average of the beam-smearing corrected dispersion field.
We make use of tabulated data from this survey, but use clear symbols throughout the plots in \cref{subsec:redshift_evolution} to highlight the difference in selection critera.

@@

\subsection{KMOS$^{3D}$ ($z\sim1.0$ and $z\sim2.3$)}\label{subsec:kmos_3d}
The KMOS$^{3D}$ results described in \cite[W15]{Wisnioski2015} describe KMOS H$\alpha$ observations of $\sim191$ massive SFGs across two redshift slices. 
At $z \sim 1.0$ the galaxies have $log(M_{\star}[M_{\odot}])=10.7$ and at $z \sim 2.3$ the median is $log(M_{\star}[M_{\odot}])=10.9$, approaching an order of magnitude above the KDS median of $log(M_{\star}[M_{\odot}])=10.0$.   The rotation velocity are taken as $V_{C} = \frac{1}{2sin(i)}(v_{obs_{max}} - v_{obs_{min}})$ and $\sigma_{int}$ is extracted from the $\sigma_{obs}$ map far from the kinematic centre, where the effects of beam-smearing are negligible.
No tabulated values are provided, and so we make use of values quoted in W15 at both redshift intervals throughout the \cref{subsec:redshift_evolution} plots.

>>>>

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
%\author[O.J. Turner et al.]{
%O. J. Turner,$^{1,2,\thanks{E-mail: turner@roe.ac.uk (OJT)}}$
%M. Cirasuolo,$^{1,2}$
%C. M. Harrison,$^{2,3}$
%J. Dunlop,$^{1}$
%R. J. McLure,$^{1}$\newauthor
%A. M. Swinbank$^{3,4}$
%H. L. Johnson$^{3,4}$
%D. Sobral$^{5}$
%J. Matthee$^{6}$
%R. M. Sharples$^{3,4}$
%\\
%$^{1}$SUPA\thanks{Scottish Universities Physics Alliance}, Institute for Astronomy, University of Edinburgh, Royal Obervatory, Edinburgh EH9 3HJ\\
%$^{2}$European Southern Observatory, Karl-Schwarzschild-Str. 2, 85748 Garching b. M{\"u}nchen, Germany\\
%$^{3}$Centre for Extragalactic Astronomy, Durham University, South Road, Durham, DH1 3LE, U.K.\\
%$^{4}$Institute for Computational Cosmology, Durham University, South Road, Durham, DH1 3LE, U.K.\\
%$^{5}$Department of Physics, Lancaster University, Lancaster, LA1 4BY, U.K.\\
%$^{6}$Leiden Observatory, Leiden University, PO Box 9513, NL-2300 RA Leiden, the Netherlands}

@@

The picture is complicated by the addition of major and minor galaxy mergers which can rapidly change the physical properties of galaxies \citep[e.g.][]{Toomre1977,Lotz2008,Conselice2011,Conselice2014} and the relative importance of in-situ, secular stellar mass growth vs. stellar mass aggregation via mergers is the subject of much work involving both observations and simulations \citep[e.g.][]{Robaina2009,Kaviraj2012,Stott2013,Lofthouse2016,Qu2016}. 
To account for the growing number density of quiescent galaxies from z$\sim 2.5$ to the present day \citep[e.g.][]{Bell2004,Faber2007,Brown2007,Ilbert2010,Brammer2011,Muzzin2013,Buitrago2013} there must also be processes which shut off star-formation within main sequence galaxies (i.e. quenching) which, to explain observations, is a function of both mass and environment \citep{Peng2010,Darvish2016}.

Recent cosmological volume simulations provide subgrid recipes for the complex interplay of baryonic processes which are at work as galaxies evolve, and can track the development of individual galaxies from early stages, to maturity and through quenching \citep{Dubois2014a,Vogelsberger2014b,Schaye2015}.
Observations can aid the predictive power of such simulations by providing constraints on the evolving physical properties of galaxy populations.
The observed dynamical properties of galaxies contain information about the transfer of angular momentum between dark matter halos and the baryons and the dissipation of this angular momentum thereafter (through gravitational collpase, mergers and outflows \citealt{Fall1983,Romanowsky2012,Fall2013}), constituting an important set of quantities for simulators to attempt to match.
Developments in both Integral-Field Spectroscopy (IFS) instrumentation and data analysis tools over the last decade have led to the observation of two-dimensional velocity and velocity dispersion fields for large samples of galaxies of different morphological types, spanning a wide redshift range \citep[e.g.][]{Sarzi2005,Flores2006,Epinat2008,ForsterSchreiber2009,Cappellari2011,Gnerucci2011,Epinat2012,Croom2012,Swinbank2012,Swinbank2012a,Bundy2015,Wisnioski2015,Stott2016,Harrison2017,Swinbank2017} and when interpreted in tandem with high-resolution imaging data from the Hubble Space Telescope ({\em {\em HST}}) these data provide exquisite information about the range of physical processes which are driving galaxy evolution.
In particular, in recent years the multiplexing capabilities of KMOS \citep{Sharples2013} have allowed for IFS kinematic observations for large galaxy samples to build up over much shorter timescales \citep{Sobral2013,Wisnioski2015,Stott2016,Mason2016,Harrison2017} providing an order of magnitude boost in statistical power over previous high-redshift campaigns.

Random motions within the interstellar medium of SFGs appear to be increasing with increasing redshift between $0 < z < 3$, as traced by their observed velocity dispersions, $\sigma_{obs}$ \citep{Genzel2008,ForsterSchreiber2009,Law2009,Cresci2009,Gnerucci2011,Epinat2012,Kassin2012,Green2014,Wisnioski2015,Stott2016}.
This has been explained in terms of increased `activity' in galaxies during and before the global peak in cosmic SFRD \citep{Madau_2014}, in the form of higher specific star formation rates (sSFR) \citep{Wisnioski2015}, larger gas reservoirs \citep{Law2009,ForsterSchreiber2009,Wisnioski2015,Stott2016}, more efficient accretion \citep{Law2009}, increased stellar feedback from supernovae \citep{Kassin2012} and turbulent disk instabilities \citep{Law2009,Bournaud2007,Bournaud2016}, all of which combine to increase $\sigma_{obs}$ and complicate its interpretation.

@@

This paper focusses on the third question by deriving and interpreting the spatially resolved kinematics of the KDS galaxies, particularly the rotation velocities and velocity dispersions, using the [O~{\sc III}]$\lambda$5007 emission line, discussing what we can learn about the nature of galaxy formation at $z \sim 3.5$ and forming evolutionary links with lower redshift work.
We seek also to minimise the impact of systematic differences introduced by the differing approaches in defining and extracting kinematic parameters when interpreting these trends.  
By making use of KMOS we have been able to study [O~{\sc III}]$\lambda$5007 emission in 77 galaxies with integration times ranging between 7.5-9 hours on source, with these galaxies, which span the mass range $9.5 < log(M_{\star}[M_{\odot}]) < 10.5$, roughly tripling the number of galaxies observed in IFS at $z > 3$. \\

@@

\subsubsection{GOODS-S}\label{subsubsec:sample_selection_goods}

Two of the FIELD environment pointings (GOODS-S-P1;GOODS-S-P2; see Table \ref{tab:pointings}) are selected within GOODS-S region \citep{Guo2013}; accessible from the VLT and with excellent multi-wavelength coverage, including deep {\em HST WFC3 F160W} imaging with $ 0.06^{\prime\prime}$ pixel scale and $ \sim 0.2^{\prime\prime}$ PSF, which is well suited for constraining galaxy morphology \citep{Grogin2011,Koekemoer2011}.
We select targets from the various spectroscopic campaigns which have targetted GOODS-S, including measurements from VIMOS \citep{Balestra2010,Cassata2014}, FORS2 \citep{Vanzella2005,Vanzella2006,Vanzella2008} and both LRIS and FORS2 as outlined in \cite{Wuyts2009}.
These targets must be within the redshift range $3 < z < 3.8$, have high spectral quality (as quantified by the VIMOS redshift flag equal `3' or `4', and the FORS2 quality flag equal `A') and we carefully exclude those targets for which the [O~{\sc III}]$\lambda$5007 or H$\beta$ emission lines, observable in the K-band at these redshifts, would be shifted into a spectral region plagued by strong OH emission.
The galaxies which remain after imposing these criteria are distributed across the GOODS-S field, and we select two regions where $\sim 20$ targets can be allocated to the KMOS IFUs (noting that the IFUs can patrol a $7.2^{\prime}$ diameter patch of sky during a single pointing).
In GOODS-S-P1 and GOODS-S-P2 we observe 20 and 17 galaxies respectively.\footnote{We note that the number of observed galaxies in GOODS-S-P2 does not include two targets which were later found to have $z < 0.5$.}

\subsubsection{SSA22}\label{subsubsec:sample_selection_ssa}
A single CLUSTER environment pointing (SSA22-P1; see Table \ref{tab:pointings}) is selected from the SSA22 field, \citep{Steidel1998,Steidel2000,Steidel2003,Shapley2003}, which, as mentioned above, is an overdensity of LBG candidates at $z \sim 3.09$.
Hundreds of spectroscopic redshifts have been confirmed for these LBGs with follow up observations using LRIS \citep{Shapley2003,Nestor2013}.
A combination of deep {\em B,V,R} band imaging with the Subaru Suprime-Cam \citep{Matsuda2004}, deep narrow band imaging at 3640$\AA$ \citep{Matsuda2004} and at 4977$\AA$ \citep{Nestor2011,Yamada2012a} and archival {\em HST ACS} and {\it WFC3} provides ancillary data in excellent support of integral field spectroscopy, albeit over a shorter wavelength baseline and with shallower exposures than in the GOODS-S field.
Fortunately at $z \sim 3.09$ the [O~{\sc III}]$\lambda$5007 line is shifted into a region of the K-band which is free from OH features and so for the CLUSTER environment pointing we fill the KMOS IFUs with galaxies located towards the centre of the SSA22 protocluster (SSA22-P1).

@@

We plot the relationship between $V_{C}$ and $M_{\star}$ for the isolated field sample in the left panel of Figure \ref{fig:tf_relation}.
In \cite{Harrison2017}, the inverse stellar mass Tully-Fisher relation relation is fit to $\sim400$ $9.5 < log(M_{\star}[M_{\odot}]) < 10.5$ star-forming galaxies at $z\sim0.9$, measured to be rotationally dominated with $V_{C}/\sigma_{int} > 1$.
The data are used to constrain parameters `a' and `b' in the equation $logV_{C}=b+a[logM_{\star} - 10.0]$ (see their section 4.2) finding $a = 0.33 \pm 0.11$ and $b = 2.12 \pm 0.04$.
We plot this best fit relation with the solid green line, with the green shaded region giving the typical scatter of 0.2 dex along the velocity axis.
These $z\sim0.9$ parameters are consistent with the coefficients measured in the local universe, $a_{z=0} = 0.278 \pm 0.010$ and $b_{z=0} = 2.142 \pm 0.004$ , for a sample of $z<0.1$ disks from \cite{Reyes2011}, which are in a similar mass range to KROSS and traced with H$\alpha$ emission.
In \citep{Reyes2011} $V_{C}$ has been extracted at the same radius and we plot this $z\sim 0.1$ local relation as the dashed black line in the left panel of Figure \ref{fig:tf_relation}.
The agreement between these parameters derived at $z\sim0$ and $z\sim0.9$ suggests that there is no evolution of the slope/normalisation of the stellar mass Tully-Fisher relation for rotationally dominated star-forming galaxies between these limits. \\

@@

Throughout \cref{sec:results} we have investigated the derived kinematic parameters of the isolated field sample, showing first that within the scatter the rotation dominated galaxies sit on a rotation velocity - stellar mass relationship consistent with what is observed in the local universe.
The mean rotation velocity of the isolated field sample is low as a result of averaging over a sample containing a large number of dispersion dominated galaxies ($66\%$ of the sample) and probable pressure support from turbulent motions \citep[e.g.][]{Burkert2010} partially supporting gravity.
This increased number of dispersion dominated galaxies in comparison to at low and intermediate redshifts appears to be driven by high velocity dispersions at $z\sim3.5$.
In this section we discuss possible physical origins for the elevated random motions traced by $\sigma_{int}$ and their impact on the galactic dynamics.

@@

The $\sigma_{int}$ shifted galaxies in Figure \ref{fig:sigma_shifted} are consistent with a single relation for the increase in velocity dispersion with redshift as a result of increasing gas fractions, with the difference between the slopes in the left and right panels highlighting the role of stellar mass in the kinematic settling of galaxies between $z\sim2$ and the local universe. 
The isolated field sample data, in combination with comparison sample results spanning $z=0-3$, thus suggest that the time evolution of the velocity dispersion measured from ionised gas emission lines is intimately linked to the consumption of gas and the accumulation of stars in a stable disk \citep[e.g.][]{Law2009,Law2012b,Law2012c,Wisnioski2015}.
Rotation dominated galaxies become less representative of the typical star-forming population at these redshifts as a result of the increased velocity dispersions as shown in Figure \ref{fig:rdf_and_v_sigma_w_redshift}, constituting only $\sim1/3$ of the isolated field sample at $z\sim3.5$.
This suggests we are probing more chaotic and unstable systems subject to gravitational instabilities and collapse on the disk scale \citep{Burkert2010,Genzel2011}, residing in a much more active period of the universe in terms of both accretion and star-formation.
Recent results indicate that these systems become strongly baryon-dominated on the galaxy disk scale at high redshift \citep{Ubler2017,Lang2017,Genzel2017}, which may imply that the increasing contribution of dark matter to galaxy disks with decreasing redshift plays a role in the evolution of velocity dispersions.

The precise interpretation of the velocity dispersion remains unclear, although there is mounting evidence that random motions have an increasingly significant contribution to the mass budget of high-redshift galaxies \citep[e.g.][]{Kassin2007,Law2009,Burkert2010,Kassin2012,Wuyts2016b,Lang2017,Ubler2017,Genzel2017}.
The nature of dispersion dominated galaxies at high-redshift has been discussed in \cite{Newman2013} using Adaptive-Optics (AO) and seeing limited observations of the same galaxies.
The AO observations show that in some cases galaxies which are clasified as dispersion dominated with seeing limited observations reveal much larger velocity gradients at higher spatial resolution.
This highlights that beam-smearing effects can wash-out observed rotational motions, particularly for small galaxies.
We have attempted to account for beam smearing using half-light radius and velocity gradient dependent dynamical modelling, but we acknowledge that these observations are challenging and cannot rule out the presence of unresolved velocity gradients in our seeing-limited dataset.
Smaller galaxies do have intrinsically smaller rotation velocities, whilst there is no observed dependence of velocity disperion on galaxy size \citep[e.g.][]{Newman2013}.
Dispersion dominated galaxies are therefore likely to be at an earlier evolutionary stage and unstable to gravitational instabilities which generate turbulence which is then maintained by the potential energy of the gas in the disk \citep{Burkert2010,Newman2013}.

@@

In sum, the isolated field sample galaxies are diverse and kinematically premature, with $\sim2/3$ of the sample being dominated by random motions which may contribute to supporting a portion of the dynamical mass \citep[e.g.][]{Kassin2007,Burkert2010,Kassin2012,Newman2013,Straatman2017,Ubler2017,Lang2017}.
In the context of the equilibrium model explored here, these galaxies will evolve gradually with redshift along the velocity-mass relationship into stable disk galaxies which have converted their gas reservoirs into stellar mass \citep[e.g.][]{Lilly2013,Tacconi2013,Wisnioski2015,Tacconi2017}. 
Future work at higher resolution and redshift will trace the extent to which gas-derived velocity dispersions trace the stellar dispersions and will investigate even earlier and more chaotic stages in the lifetimes of late-type galaxies.

@@

\begin{table*}
\centering
\begin{threeparttable}
\caption{We present here a reference of the mean and median kinematic properties used throughout figures \protect\ref{fig:tf_relation}, \protect\ref{fig:sigma_and_v_sigma_w_redshift} and \protect\ref{fig:rdf_and_v_sigma_w_redshift} for the different surveys.
The errors on the mean represent the statistical errors from bootstrap resampling and the lower and upper errors on the medians are the 16th and 84th percentiles of the distribution respectively.}
\label{tab:evolution_numbers}
\begin{tabular}{c c c c c c c c c c }

@@

We make use of tabulated data from the surveys deemed directly comparable, where available, to compute sample averages using the following method. 
Throughout \cref{sec:results} we highlight in the figures which values can be directly compared using filled and hollow symbols.
The fractional error weighted mean of $V_{C}/\sigma_{int}$, $\sigma_{int}$ and $V_{C}$ in each of the samples is computed (i.e. we do not want the derived values with extremely large errors to dominate the averages).
The errors on these mean values are computed in a statistical sense, by generating bootstrapped samples, with replacement, with size equivalent to the original survey sample size and with values perturbed by a random number drawn from a gaussian distribution with width given by the error on the original point.
The same process is applied to compute the errors on the sample medians and we report the 16th and 84th percentiles of the distributions of each of the above quantities as an indicator of the distribution width, and hence galaxy diversity, at each redshift slice.
These results are listed in Table \ref{tab:evolution_numbers} and discussed in detail throughout \cref{sec:results}, where we will make statements about dynamical evolution by connecting the dots of these different surveys, assuming that on average they are tracing a population of SFGs which evolve across cosmic time.

@@

\subsection{DYNAMO ($z\sim0.1$, but selected with physical properties resembling $z\sim2$)}\label{subsec:DYNAMO}
In the DYNAMO survey \citep[G14]{Green2014}, H$\alpha$ IFU data of 67 galaxies with median $log(M_{\star}[M_{\odot}])=10.3$ at $z\sim0.1$ is presented.
The selection criteria is such that half of the sample have high sSFR representative of SFGs at $z\sim 2$, and are also found to have higher $f_{gas}$ values than locally, mimicking the physical conditions of $z\sim 2$ SFGs.
$V_{C}$ values are extracted at a fixed radius from an arctangent model fit to the velocity fields ($1.6R_{1/2}$ as measured in the r-band) and $\sigma_{int}$ is taken as the luminosity weighted average of the beam-smearing corrected dispersion field.
We make use of tabulated data from this survey, but use clear symbols throughout the plots in \cref{sec:results} to highlight the difference in selection critera.

@@

\subsection{KMOS$^{3D}$ ($z\sim1.0$ and $z\sim2.3$)}\label{subsec:kmos_3d}
The KMOS$^{3D}$ results described in \cite[W15]{Wisnioski2015} describe KMOS H$\alpha$ observations of $\sim191$ massive SFGs across two redshift slices. 
At $z \sim 1.0$ the galaxies have $log(M_{\star}[M_{\odot}])=10.7$ and at $z \sim 2.3$ the median is $log(M_{\star}[M_{\odot}])=10.9$, approaching an order of magnitude above the KDS median of $log(M_{\star}[M_{\odot}])=10.0$.   The rotation velocity are taken as $V_{C} = \frac{1}{2sin(i)}(v_{obs_{max}} - v_{obs_{min}})$ and $\sigma_{int}$ is extracted from the $\sigma_{obs}$ map far from the kinematic centre, where the effects of beam-smearing are negligible.
No tabulated values are provided, and so we make use of values quoted in W15 at both redshift intervals throughout the \cref{sec:results} plots.
